### 2017-03-29 paper/evaluation.tex
added missing plot

\vspace{-3ex}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjects/subjects.pdf}
    \caption{\label{fig:subjects}\Fix{this is mocked data!}}
\end{figure}
\vspace{-2ex}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  Also, measured the
approximated overhead from the build system after skipping non-related
tasks. We identified the generated test reports and compared the
difference between the elapsed time reported from Maven and the sum of
all test cases executed.
To avoid noise from operating system events, we used a dedicated
server remotely via SSH with the operating system running only
essential services (\eg, the SSH server). In addition, we configured
the \CodeIn{isolcpus} option from the Linux Kernel \cite{linux-kernel}
to isolate six virtual CPUs to execute our experiment and the
remaining CPUs to run the operating system. By isolating a set of
virtual CPUs, we prevent context-switching from experiment processes
and OS-related processes.

>>>>

\vspace{-3ex}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/plot-subjects/subjs.pdf}
    \caption{\label{fig:subjects}\Fix{this is mocked data!}}
\end{figure}
\vspace{-2ex}

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests. \Jbc{The following
steps may change $\rightarrow$}
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we configured the \CodeIn{isolcpus} option
from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
to execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from experiment processes and OS-related processes.
